The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-17 dit-paper_ieee.tex
small reformulations

		This system is guaranteed to have at least one solution modulo $H$ for given
		values of $a_i$ if the following condition is respected:
		%Review 3 : use ref to justify this formula
		\begin{equation}
			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i, T_j)) \; \forall i,j
		\end{equation}
		which means that there could be systems with no FPDIT.
		We now present an example of such a system.\\

@@

		However this is very inefficient as there are exponentially many different
		combinations of $a_i$ values in the number of tasks, and resolving
		exponentially many CRP is prohibitively slow. A faster method for finding
		the FPDIT consists in merging all these CRP instances into one problem
		(finding all DITs), which can be solved faster by
		Algorithm~\ref{alg:multiACRP}, as a significant part of the needed
		intermediate results are shared between instances.

>>>>

		This system is guaranteed to have at least one solution modulo $H$ for given
		values of $a_i$ if the following condition is respected:
		%Review 3 : use ref to justify this formula
		\begin{equation}
			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i, T_j)) \; \forall i,j
		\end{equation}
		which means that systems where no such values of $a_i$ exists do not have a FPDIT.
		We now present an example of such a system.\\

@@

		However this is very inefficient as there are exponentially many different
		combinations of $a_i$ values in the number of tasks, and resolving
		exponentially many CRP is prohibitively slow. A faster method for finding
		the FPDIT consists in merging all these CRP instances into one problem
		(finding all DITs), which can be solved faster by
		Algorithm~\ref{alg:multiACRP}, as a significant part of the
		intermediate results are shared between instances.
